Predicting the Quality of CDRH3 Antibody Loop Structural Models

### 2022-10-05 paper.tex
Centred all figures and full width
Added more macros

\documentclass[12pt]{article}
\bibliographystyle{unsrt}
\usepackage{a4}
\usepackage{graphicx}
\usepackage{url}
\newcommand{\ca}{\mbox{C$\alpha$}}

@@

\begin{figure}
  \includegraphics[scale=1]{loopdist.eps}
  \centering
  \caption { Distribution of CDR-H3 loop lengths in mouse (left),
    human (centre) and cow (right). Mouse and human antibody CDR-H3s
    have a unimodal, yet almost normal distribution with a range of
    $\sim$4--28 and 4--38 respectively. The length cut-off for CDR-H3s
    depicted above is 30 amino acids. Bovine antibodies with
    significantly longer CDR-H3 loops than depicted here exist,
    reaching a length of 67 amino acids and
    above\protect\cite{Wong2015}.}  
  \label{fig:loopdist}
\end{figure}

@@

In this project abYmod is used, which is to be found at
\url{http://abymod.abysis.org/}. The program utilizes extensive canonical
class definitions, VH/VL angle prediction and a large database of loop
structures (LoopDB) for CDR-H3 modelling to achieve optimal
results. Upon inputting an antibody sequence, abYmod assigns the
canonical class using a set of key residues\cite{Martin1996}and where
an exact match is not possible, a nearest match is made. Then, the
program identifies the 10 best overall-matching PDB files according to
sequence identity for the light and heavy chain. Of these, the best
template is then identified for each CDR using sequence similarity and
identity. In general, modelling the antibody using the single best
overall-matching template works best and the CDR-specific templates
are used if there is no canonical match. The VH/VL packing angle is
then determined either using machine learning or the chosen template
structure for one of the chains. CDR specific templates, if selected,
are grafted onto the framework. If there is no template of the correct
length for CDR-H3, the loop is built using the LoopDB database,
containing CDR-H3-like loops from all proteins. Finally, Gromacs energy
minimization software is used to optimize the model. This method has
proven very effective and preliminary analysis suggests the method
achieves comparable results or outperforms other modelling software
(see results section).

@@

\begin{figure}
  \centering
  \includegraphics[scale=0.3]{AMA.eps}
  \caption {RMSD values of the CDR-H3 loop for structures from the
    Antibody Modelling Assessment I (2011) and AMAII (2014). abYmod
    outperforms other modelling software in some instances, but also
    has much lower accuracy in few outlier cases. (left: an abYmod
    structure for C705 could be generated, yet the RMSD calculation
    failed. Right: Ab01 is the rabbit antibody PDB:4MA3, which was
    excluded in the CDR-H3 modelling stage in AMAII due to
    difficulties modelling the overall structure previously. Ab01 is
    shown for the methods, where generated models were adequate for
    RMSD calculation.)}
  \label{fig:AMA}
\end{figure}

@@

\begin{figure}
  \includegraphics[scale=0.9]{logo.eps}
  \caption {Sequence Logo of the CDR-H3 loop sequence. Data on amino
    acid occurrence taken from \protect\url{http://abymod.abysis.org/} Visualized
    using Seq2Logo.}
  \label{fig:logo}
\end{figure}

@@

\subsection{Feature Calculations}
\begin{figure}
  \centering
  \includegraphics[scale=0.49]{feature_table.eps}
  \caption {A summary of how different feature values were calculated.}
  \label{fig:feature_table}
\end{figure}

\begin{figure}
  \includegraphics[scale=0.6]{angle.eps}
  \caption {Diagram visualizing the process underlying the protrusion
    calculation. First, the base residues (i.e.\ H95 and H102, shown as
    red spheres) of the CDR-H3 (shown in red) are identified. Then, a
    line is drawn between the two \ca\ atoms of these residues (yellow
    dashed line). The distance of the \ca-atom of each residue in the
    CDR-H3 loop to this line is calculated. The residue which has the
    greatest distance to the line (shown as green sphere) is outputted
    as one-letter amino acid code and used as feature. The distance in
    \AA\ (depicted as yellow arrow) is used as the `protrusion'
    feature.}
  \label{fig:angle}
\end{figure}

\begin{figure}
  \includegraphics[scale=0.45]{method.eps}
  \caption {Simplified pipeline for creating the final machine
    learning model that will predict model quality by giving its RMSD
    range.}
  \label{fig:method}
\end{figure}

>>>>

\documentclass[12pt]{article}
\bibliographystyle{unsrt}
\usepackage{a4}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}
\newcommand{\ca}{\mbox{C$\alpha$}}
\newcommand{\VH}{\mbox{V\kern-.1667em \lower.5ex\hbox{\scriptsize H}}}
\newcommand{\VL}{\mbox{V\kern-.1667em \lower.5ex\hbox{\scriptsize L}}}
\newcommand{\VHVL}{\mbox{\VH/\VL}}
\newcommand{\CH}[1]{\mbox{C\lower.5ex\hbox{\scriptsize H}#1}}
\newcommand{\CL}{\mbox{C\kern-.0833em \lower.5ex\hbox{\scriptsize L}}}
\newcommand{\FV}{\mbox{\it Fv}}
\newcommand{\Fab}{\mbox{\it Fab}}

\newcommand{\e}[1]{\mbox{$\times 10^{#1}$}}
\newcommand{\etal}{~\emph{et al.}}
\newcommand{\degree}{\mbox{${}^{\circ}$}}
\newcommand{\lilian}[1]{{\color{red}\sout{#1}}}
\newcommand{\andrew}[1]{{\color{green}\uline{#1}}}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{loopdist.eps}
  \caption { Distribution of CDR-H3 loop lengths in mouse (left),
    human (centre) and cow (right). Mouse and human antibody CDR-H3s
    have a unimodal, yet almost normal distribution with a range of
    $\sim$4--28 and 4--38 respectively. The length cut-off for CDR-H3s
    depicted above is 30 amino acids. Bovine antibodies with
    significantly longer CDR-H3 loops than depicted here exist,
    reaching a length of 67 amino acids and
    above\protect\cite{Wong2015}.}  
  \label{fig:loopdist}
\end{figure}

@@

In this project abYmod is used, which is to be found at
\url{http://abymod.abysis.org/}. The program utilizes extensive canonical
class definitions, \VHVL\ angle prediction and a large database of loop
structures (LoopDB) for CDR-H3 modelling to achieve optimal
results. Upon inputting an antibody sequence, abYmod assigns the
canonical class using a set of key residues\cite{Martin1996}and where
an exact match is not possible, a nearest match is made. Then, the
program identifies the 10 best overall-matching PDB files according to
sequence identity for the light and heavy chain. Of these, the best
template is then identified for each CDR using sequence similarity and
identity. In general, modelling the antibody using the single best
overall-matching template works best and the CDR-specific templates
are used if there is no canonical match. The \VHVL\ packing angle is
then determined either using machine learning or the chosen template
structure for one of the chains. CDR specific templates, if selected,
are grafted onto the framework. If there is no template of the correct
length for CDR-H3, the loop is built using the LoopDB database,
containing CDR-H3-like loops from all proteins. Finally, Gromacs energy
minimization software is used to optimize the model. This method has
proven very effective and preliminary analysis suggests the method
achieves comparable results or outperforms other modelling software
(see results section).

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{AMA.eps}
  \caption {RMSD values of the CDR-H3 loop for structures from the
    Antibody Modelling Assessment I (2011) and AMAII (2014). abYmod
    outperforms other modelling software in some instances, but also
    has much lower accuracy in few outlier cases. (left: an abYmod
    structure for C705 could be generated, yet the RMSD calculation
    failed. Right: Ab01 is the rabbit antibody PDB:4MA3, which was
    excluded in the CDR-H3 modelling stage in AMAII due to
    difficulties modelling the overall structure previously. Ab01 is
    shown for the methods, where generated models were adequate for
    RMSD calculation.)}
  \label{fig:AMA}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{logo.eps}
  \caption {Sequence Logo of the CDR-H3 loop sequence. Data on amino
    acid occurrence taken from \protect\url{http://abymod.abysis.org/} Visualized
    using Seq2Logo.}
  \label{fig:logo}
\end{figure}

@@

\subsection{Feature Calculations}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{feature_table.eps}
  \caption {A summary of how different feature values were calculated.}
  \label{fig:feature_table}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{angle.eps}
  \caption {Diagram visualizing the process underlying the protrusion
    calculation. First, the base residues (i.e.\ H95 and H102, shown as
    red spheres) of the CDR-H3 (shown in red) are identified. Then, a
    line is drawn between the two \ca\ atoms of these residues (yellow
    dashed line). The distance of the \ca-atom of each residue in the
    CDR-H3 loop to this line is calculated. The residue which has the
    greatest distance to the line (shown as green sphere) is outputted
    as one-letter amino acid code and used as feature. The distance in
    \AA\ (depicted as yellow arrow) is used as the `protrusion'
    feature.}
  \label{fig:angle}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{method.eps}
  \caption {Simplified pipeline for creating the final machine
    learning model that will predict model quality by giving its RMSD
    range.}
  \label{fig:method}
\end{figure}
